External Patch Group Prior Guided Internal Orthogonal Dictionary Learning for Real Image Denoising

### 2016-10-26 CVPR2017_Review_Unified.tex
add

\section{External Patch Group Prior Guided Internal Orthogonal Dictionary Learning}
In this section, we formulate the framework of external Patch Group prior guided internal subspace learning. We first introduce the patch group prior leaning on clean natural RGB images. Then we formulate the external guided internal subspace learning. Finally, we discuss the differences between external subspaces and the corresponding internal subspace.

>>>>

\section{External Patch Group Prior Guided Internal Orthogonal Dictionary Learning}
In this section, we formulate the framework of external patch group (PG) prior guided internal orthogonal dictionary learning. We first introduce the patch PG leaning on clean natural RGB images. Then we propose to exploy the external PG prior to guide the internal clustering and orthogonal dictionary learning (DL). The orthogonal DL has alternative closed-form solutions in term of updating sparse coefficients and dictionary. Finally, we discuss the advantages of our proposed external PG prior guided internal orthogonal dictionary learning algorithm.
